Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-02-11 paper/main.tex
Updates

\begin{figure}
	\centering
	\begin{tabular}{llrl}
		$X$ & $Y$ & $ \bm{Z} $ & p-value \\
		\hline
		Incm & MrtS &  Age, Occp, Rltn & $ 0.29 $     \\
		Incm & Sex  &  Occp, Rltn      & $ 0.21 $     \\
		Incm & Wrkc &  Occp 	       & $ 1.5e^{-3} $ \\
		Edct & MrtS & Incm, Occp, Rltn & $ 0.02 $       \\
		\hline
	\end{tabular}
	\caption{Results of testing some of implied CIs of the DAG in
		 Figure~\ref{fig:intro}(b) using the same CI test that was used for
		 learning it.}
	\label{fig:ci_table}
\end{figure}

>>>>

\begin{figure}
	\centering
	\begin{tabular}{llrl}
		$X$ & $Y$ & $ \bm{Z} $ & p-value \\
		\hline
		Incm & MrtS &  Age, Occp, Rltn & $ 0.29 $     \\
		Incm & Sex  &  Occp, Rltn      & $ 0.21 $     \\
		Incm & Wrkc &  Occp 	       & $ 1.5e^{-3} $ \\
		Edct & MrtS & Incm, Occp, Rltn & $ 0.02 $       \\
		\hline
	\end{tabular}
	\caption{Results of testing some of the implied CIs of the DAG in
		 Figure~\ref{fig:intro}(b) using the same residualization based
	 	 CI test that was used for learning it.}
	\label{fig:ci_table}
\end{figure}
